Noun Learning as Network Growth: A Cross-linguistic Analysis

### 2019-02-06 journal/ms.Rmd
second version journal

---
title             : "Word Learning as Network Growth: A Cross-linguistic Analysis"
shorttitle        : "Word Learning as Network Growth"
#numbersections: true

@@

keywords          : "Language understanding; audio-visual processing; word learning; speech perception; computational modeling."

@@

Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) was also found to predict the Age of Acquisition (AoA) of words. The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975; @luce1998]. Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008]. These studies have generally found that children tend to produce words that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon.  In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition. For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT). Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.

<!-- For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983]. -->
These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left). Thus, the network structure is a causal factor in early word learning, that is, children rely on the organization of their past knowledge to determine future learning [@storkel2009; @altvater2013; @chi1983; @borovsky2016]. In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right). Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input. For example, highly connected words in the input could be more easily learned because of their contextual diversity, allowing for an easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015]. Another reason could be that these words are emphasized by the cargivers in their child-directed speech [@huttenlocher1991; @hoff2002; @clark2007].

@@

@hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesised by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known. However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized. However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only. The extent to which this result depends on the domain (e.g., semantic vs. phonological connectivity), the vocabulary measure (production vs. comprehension) and culture/language is still unclear. In this work, we test the generality of the finding along these three dimensions.

First, we study the phonological network in addition to the semantic network. These two networks represent different ways the mental lexicon is structured [@beckage2016]. In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa. Does the phonological network also predict word learning? Previous work did find an effect of words' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014]. In other words, words learned earlier in life tend to sound similar to many other words than a word learned later in life. However, this finding is *a priori* compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.  Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
<!--
The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains. -->

Second, we study vocabularies measured using both comprehension and production. Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition [@benedict1979; @fenson94]. These differences may reflect the fact that comprehension and production do not share the same constraints. For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky2016]. By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.

@@

We adopted the following research strategy. We used a cross-linguistic dataset of children's vocabulary development [@frank2017; @fenson94], and we studied the timeline of word learning using the normative/average age of acquisition (i.e., the age at which at least 50% of children know a given words). Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies. Children may vary in their individual learning trajectories, but the aggregate data provide highly robust measures of the average learning patterns [@fenson94]. The use of such measures has lead to important insights on the mechanisms of word learning [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016].

The paper is organized as follows. First, we describe the datasets we used and explain how we constructed the networks. Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties infom hypotheses about network growth. Next, we explicitly fit the two hypothesized growth mechanisms to the data. We investigate the extent to which the results obtained in @hills2009 generalize to phonological networks and comprehension-based vocabularies, and whether this generalization holds cross-linguistically.

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. Due to these limitations, we use data from younger children to test comprehension and data from older children to test production. Following previous studies [@storkel2009; @hills2009], we restrict our analysis to the category of nouns.\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}. Table \@ref(tab:stats) gives an overview of the data we used.

@@

We constructed semantic networks for English data following the procedure outlined in @hills2009, as follows. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based the prior work by @hills2009 stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated for indegree.} To model growth from month to month, we constructed a different network at each month, based on the words that have been acquired by that month.

Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages. Using the same association data across languages does not necessarily lead to similar networks. Indeed, though this approximation assumes that the semantic similarity measure is universal–which is a reasonable approximation [e.g., @youn2016], the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.

@@

To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/).** We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017]. However, these studies reported a contribution of phonological connectivity to word learning when networks were built using a rich adult vocabulary. Since the focus of the current study is on the mechanism of growth, the networks should be based on children's early vocabulary. The latter, however, contains very few word pairs with an edit distance of 1. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker than those obtained with a threshold of 2. We did not consider the case of a threshold larger than 2 since the pairs will become less and less phonologically related.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

@@

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months). This global network is the end-state towards which both INT and EXT converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.  In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had both semantic and phonological information in each language.

@@

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also necessary to INT, although the causality is reversed: higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT. If there is no such correlation, neither growth scenario can be posited as a possible learning mechanism.

Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` (SD=`r ps_sd`) for the semantic networks and `r pp_ave` (SD=`r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` (SD=`r cs_sd`) for the semantic networks and `r cp_ave` (SD=`r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English (e.g., Storkel 2004, 2009; Hills et al. 2009) and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.

@@

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. As was suggested by @arbesman2010, these "truncated" power-laws in phonological networks may reflect the various constraints that exist on word formation in the phonological domain such as the number of phonemes in the language, the phonotactics (i.e., the way sound sequences are arranged in words), and the length of words. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law.

@@

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilistic programming language  WebPPL [@dippl]. We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \@ref(fig:growthPred).

First, the results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Second, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather it supports our initial approximation about the universality of the semantic similarity measure. That said, this apprimation is not perfect; for example there is evidence that a small part of the variance in free assication data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.

@@

Since we found INT to be uninformative, we dropped it from this analysis, keeping only EXT. This simplified the model because we no longer needed to fit growth month-by-month. The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network. A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting linear regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.

For word length, we counted the number of phonemes in our generated IPA transcription. For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014]. For each word, counts included words that shared the same stem  (e.g., "cats" counts as "cat"), or words that were synonymous (e.g. "father" counts as "daddy"). Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008 for a similar research strategy].

@@

The findings for the new predictors were as follows. Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015]. Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., under review). Thus, word length seems to reflect the effects of production's constraints rather than than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.

As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences. Connectivity contributes to learning in some languages but not in other. In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This contrasts with the original finding in @hills2009. However, this might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset. That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \@ref(fig:staticAll)).

@@

This study provided an analysis of network growth during development. We compared two network growth scenarios described in the pioneering work of @steyvers2005 and @hills2009.  The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns. These two mechanisms represent two fundamentally different accounts of lexical growth: One suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized. The present study tested the generality of previous findings [@hills2009; @hills2010] by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.

@@

For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @pinker2013; @yurovsky2015]. According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings. In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.  This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts. Crucially, children can learn these words without necessarily knowing the meaning of all other words with witch they co-occur (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@hills2010].

In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking lwo level statistical patterns, e.g., high probability sound sequences. Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001]. This explanation is supported by computational simulations that show how learning general phonotactics patterns create ``well-worn paths'' which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].

>>>>

---
title             : "Noun Learning as Network Growth: A Cross-linguistic Analysis"
shorttitle        : "Noun Learning as Network Growth"
#numbersections: true

@@

keywords          : "Word learning; semantic network; phonological network; network growth; cross-linguistic analysis."

@@

Besides word-level properties, the structure of the lexicon (that is, how words relate to one another) was also found to predict the Age of Acquisition (AoA) of words. The lexical structure can be characterized in terms of a network where each node represents a word in the vocabulary, and each link between two nodes represents a relationship between the corresponding pair of words [e.g., @collins1975; @luce1998]. Previous studies have investigated early vocabulary structure by constructing networks using  a variety of word-word relations including shared semantic features [@mcrae2005], target-cue relationships in free association norms [@nelson1998], co-occurrence in child directed speech [@macwhinney2014], and phonological relatedness [@vitevitch2008]. These studies have generally found that children tend to produce nouns that have higher neighborhood density (i.e., high connectivity in the network) earlier, both at the phonological and the semantic level [@storkel2009; @hills2009; @hills2010; @stella2017; @carlson2014].

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment, highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts learning is the *internal* connectivity in the child's early lexicon.  In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition. For clarity of reading, we will call preferential attachment the Internally-driven mechanism (INT), and preferential acquisition the Externally-driven mechanism (EXT). Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network.

<!-- For example, having a rich and organized knowledge about the domain of dinosaurs would facilitate the acquisition of new dinosaur-related words [@chi1983]. -->
These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the INT proposal, learning is driven by known words with high connectivity to other known words (Figure 1, left). Thus, the network structure is a causal factor in word learning, that is, children rely on the organization of their past knowledge to determine future learning [@storkel2009; @altvater2013; @chi1983; @borovsky2016]. In contrast, on the EXT approach, learning is driven by the connectivity of words that are not known yet (Figure 1, right). Thus, the relevant network structure is not internally represented by children, and the observed connectivity effect might be an epiphenomenon of some properties of the linguistic input. For example, highly connected concrete nouns in the input could be more easily learned because of their contextual diversity, allowing for an easier meaning disambiguation [@smith2008; @mcmurray2012; @yurovsky2015]. Another reason could be that these words are emphasized by the caregivers in their child-directed speech [@huttenlocher1991; @hoff2002; @clark2007].

@@

@hills2009 investigated the growth of lexico-semantic networks in toddlers and found that growth did not proceed according to INT as was originally hypothesized by @steyvers2005, but rather according to EXT.\footnote{Besides INT and EXT, the authors tested a third mechanism (called the lure of associates) which resembles EXT in that it is driven by the connectivity of external nodes, except that this connectivity is computed with respect to words that are known. However, EXT is the externally-driven scenario that best predicted the data in this previous work.} This is an important finding because it suggests that learning in the early stages is mostly driven by properties of the external input, regardless of how past knowledge is organized. However, this work has been done in the special case of networks that are based on 1) semantic associations, 2) production-based vocabularies, and 3) data from English-learning children, only. The extent to which this result depends on the domain (e.g., semantic vs. phonological connectivity), the vocabulary measure (production vs. comprehension) and culture/language is still unclear. In this work, we test the generality of the finding along these three dimensions.

First, we study the phonological network in addition to the semantic network. These two networks represent different ways the mental lexicon is structured [@beckage2016]. In particular, words that are neighbors in the semantic network (e.g., "cat", "dog") are not necessarily neighbors in the phonological network, and vice versa. Does the phonological network also predict word learning? Previous work did find an effect of nouns' connectivity in the phonological network on their age of learning [@storkel2009; @stella2017; @carlson2014]. In other words, nouns learned earlier in life tend to sound similar to many other nouns than a word learned later in life. However, this finding is *a priori* compatible with both INT and EXT, and previous studies did not explicitly compare these two mechanisms.  Here, we investigate whether phonological networks, like semantic networks, grow through EXT, or if they rather grow via INT (Figure\ \@ref(fig:growth)).
<!--
The phonological strcuture influence word processing in adults (Vitevitch, 2008;  Chan & Vitevitch, 2009; Chan & Vitevitch,2010; Vitevitch, Chan, and Roodenrys, 2012; Castro et al. 2018). Here we test whether the mechanism of networtk growth in the phonological domains mirrors the mechanism found in the semantic domains. -->

Second, we study vocabularies measured using both comprehension and production. Previous studies have found differences between these vocabularies in terms of their content and rate of acquisition [@benedict1979; @fenson94; @bates1995]. These differences may reflect the fact that comprehension and production do not share the same constraints. For instance, whereas comprehension depends on the ease with which words are stored and accessed, production depends, additionally, on the ease with which words are articulated, e.g., shorter words are produced earlier [@braginsky2016]. By investigating comprehension-based vocabularies, we assess the extent to which the network growth mechanism captures general learning patterns beyond the specific constraints of production.

@@

We adopted the following research strategy. We used a cross-linguistic dataset of children's vocabulary development [@frank2017; @fenson94], and we studied the timeline of noun learning using the normative age of acquisition (i.e., the age at which at least 50% of children know a given words). Our choice of studying the normative learning trajectory rather than the individual trajectories was motivated by the nature of the dataset used---which is primarily based on cross-sectional studies. Children may vary in their individual learning trajectories, but the aggregate data provide highly robust measures of the average learning patterns [@fenson94]. The use of such measures has lead to important insights on the mechanisms of word learning [@storkel2009; @stella2017; @hills2009; @hills2010; @goodman2008; @braginsky2016].

The paper is organized as follows. First, we describe the datasets we used and explain how we constructed the networks. Second, we analyze static properties of words' connectivity in these networks (correlation with age of acquisition and shape of the distribution) and we explain how these properties inform hypotheses about network growth. Next, we explicitly fit the two hypothesized growth mechanisms to the data. We investigate the extent to which the results obtained in @hills2009 generalize to phonological networks and comprehension-based vocabularies, and whether this generalization holds cross-linguistically.

@@

We used data from Wordbank [@frank2017], an open repository aggregating cross-linguistic language developmental data of the MacArthur-Bates Communicative Development Inventory (CDI), a parent report vocabulary checklist. Parent report is a reliable and valid measure of children's vocabulary that allows for the cost-effective collection of datasets large enough to test network-based models of acquisition [@fenson94]. When filling out a CDI form, caregivers are either invited to indicate whether their child "understands" (comprehension) or "understands and says" (production) each of about 400-700 words. For younger children (e.g., 8 to 18 months in the English data), both comprehension and production are queried, whereas for older children (16 to 36 months) only production is queried. Due to these limitations, we use data from younger children to test comprehension and data from older children to test production. In addition, following previous studies [@storkel2009; @hills2009], we restricted our analysis to the category of nouns due to the fact that nouns predominate the early expressive and receptive lexicons [@bates1995]. Their larger sample size (compared, for example, to verbs or adjectives) is more suited to the network-based analysis of development. Table \@ref(tab:stats) gives an overview of the data we used.

<!--
 Following previous studies [@storkel2009; @hills2009], we restrict our analysis to the category of nouns.
\footnote{This choice was also forced by the fact that the great majority of association data produced by adults–and which we used to build semantic networks–were nouns.}-->

@@

We constructed semantic networks for English data following the procedure outlined in @hills2009, as follows. We used as an index of semantic relatedness the Florida Free Association Norms [@nelson1998]. This dataset was collected by giving adult participants a word (the cue), and asking them to write the first word that comes to mind (the target). For example, when given the word "ball", they might answer with the word "game". A pair of nodes were connected by a directed link from the cue to the target if there was a cue-target relationship between these nodes in the association norms. The connectivity of a given node was characterized by its *indegree*: the number of links for which the word was the target.\footnote{This choice was based on prior work by Hills et al. (2009) stating that analyses with both outdegrees (sum of the links where the word is the cue in a cue-target pair) and total degree  (outdegree plus indegree) led to results weaker than those calculated with indegree.} To model growth from month to month, we constructed a different network at each month, based on the nouns that have been acquired by that month.

Since  the free association norms are available only in English, we used the hand-checked translation equivalents available in Wordbank, which allowed us to use the English association norms across 10 languages. Using the same association data across languages does not necessarily lead to similar networks. Indeed, though this approximation assumes that the semantic similarity measure is universal---which is a reasonable approximation [e.g., @youn2016]---the set of words acquired by children as well as the timeline of this acquisition can still vary from language to language leading to possibility different learning strategies.

@@

To construct phonological networks we first mapped the orthographic transcription of words to their International Phonetic Alphabet (IPA) transcriptions in each language, using the open source text-to-speech software **[Espeak](http://http://espeak.sourceforge.net/)**. This software provides the correct IPA transcription if the word is found in a spelling-to-phonemes dictionary, otherwise it uses  language-specific pronunciation rules to generate an approximate phonetic transcription. We used the Levenshtein distance (also known as edit distance) as a measure of phonological relatedness between two nodes. The measure counts the minimum number of operations (insertions, deletions, substitutions) required to change one string into another.

In previous studies, two nodes were linked if they had an edit distance of 1 [@storkel2009; @carlson2014; @stella2017]. However, these studies reported a contribution of phonological connectivity to noun learning when networks were built using a rich adult vocabulary. Since the focus of the current study is on the mechanism of growth, the networks should be based on children's early vocabulary. The latter, however, contains very few noun pairs with an edit distance of 1. Thus, we increased the threshold from 1 to 2, that is, two nodes were related if their edit distance was equal to 1 or 2.\footnote{We also considered the case of an edit distance of 1 as well as the continuous measure, i.e., the inverse edit distance without threshold. In both cases, the results were weaker than those obtained with a threshold of 2. We did not consider the case of a threshold larger than 2 since many pairs become phonologically unrelated.} The connectivity of a given node was characterized with its *degree*: the number of links it shares with other words.

@@

We start by analyzing word connectivity in the global (static) network. We constructed this network using nouns learned by the oldest age for which we have CDI data (e.g., in English this corresponds, in comprehension, to the network by 18 months, and in production, to the network by 30 months). This global network is the end-state towards which both INT and EXT converge by the last month of learning. Moreover, following @hills2009, we used this end-state network as a proxy for the external connectivity in the learning environment. Below we analyze properties of this global networks that may a priori hint at an INT- or EXT-like growth.  In order to compare various predictors on the same data, we restrict the analysis to the subset of nouns for which we had semantic associates in the free association norms.

@@

Connectivity in the global network is directly related to EXT as it represents the explicit criterion this growth scenario uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of an EXT-like growth scenario is a correlation between connectivity in the global network and the age of acquisition. This correlation is also necessary to INT, although the causality is reversed: Higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time. Thus, the correlation between connectivity in the end-state network and AoA can result from both EXT and INT. If there is no such correlation, neither growth scenario can be posited as a possible learning mechanism.

Figures \@ref(fig:corrProd) and \@ref(fig:corrComp) show how the age of production and comprehension, respectively, correlates with the degree (or indegree for the semantic networks). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled. The plots show, overall, a negative correlation between the month of acquisition and the degree.  In production data, the average correlation across languages was `r ps_ave` ($SD=$`r ps_sd`) for the semantic networks and `r pp_ave` ($SD=$`r pp_sd`) for the phonological networks.  In comprehension data, the average correlation was `r cs_ave` ($SD=$`r cs_sd`) for the semantic networks and `r cp_ave` ($SD=$`r cp_sd`) for the phonological networks. These results indicate that nouns with higher degrees are generally learned earlier, thus replicating previous findings in English [@storkel2009; @hills2009] and extending these findings to 10 different languages, generally, in both production- and comprehension-based vocabularies.

@@

Overall, we could not reject the null hypothesis of a power-law distribution: The $p$-value was generally above 0.1 in almost all languages for both production and comprehension. That said, phonological networks had relatively larger cut-offs than semantic networks. These "truncated" power-laws  in phonological networks may be due to the constraints that exist on word formation in the phonological domain such as the size of the phonemic inventory, phonotactic rules, and word length. Such constraints may limit the number of words that are phonologically similar, thus leading to distributions which decay faster than a non-truncated power law [@arbesman2010].

@@

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilistic programming language  WebPPL [@dippl]. We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \@ref(fig:growthPred). The results replicate Hills et al.'s original finding regarding the semantic network in English and the production-based vocabulary, which is that this network grows by EXT, not by INT. Crucially, our results show that, generally speaking, this finding generalizes to comprehension-based vocabulary, and holds across languages. This generalization was obtained in both the semantic^[One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption, rather, it supports our initial approximation about the universality of the semantic similarity measure. That said, this approximation is not perfect. For example there is evidence that a small part of the variance in free association data can be explained by phonological similarity [@kachergis2011; @matusevych2018], thus leading to possibly minor cross-linguistic differences.] and phonological domains.

@@

Since we found INT to be uninformative, we dropped it from this analysis, keeping only EXT. This simplified the model because we no longer needed to fit growth month-by-month. The latter was a requirement only for INT where the words' utilities varied from month to month, depending on how connectivity changed in the growing internal network. A more direct way to assess and compare the contribution of EXT in relation to other word-level factors is through conducting regressions, where connectivity in the learning environment, frequency and length predict the age of acquisition.

For word length, we counted the number of phonemes in our generated IPA transcription. For word frequency, we used the frequency estimates from @braginsky2016 where unigram counts were derived based on CHILDES corpora in each language [@macwhinney2014]. Although these frequency counts use transcripts from independent sets of children, they are based on large samples, and this allows us to average out possible differences between children and the specificities of their input [see @goodman2008 for a similar research strategy].

@@

The findings for the new predictors were as follows. Overall, frequency is the largest and most consistent predictor of age of acquisition in both comprehension and production data and across languages, endorsing results for nouns across a variety of analyses [@goodman2008; @braginsky2016; @roy2015]. Word length is more predictive for production than comprehension (and this difference is very clear in the global model), replicating previous work (Braginsky et al., under review). Thus, word length seems to reflect the effects of production's constraints rather than comprehension's constraints, i.e., longer words are harder to articulate but they may not be significantly more difficult to store and access.

As for the factors of interest, i.e., semantic and phonological connectivity, we found cross-linguistic differences. Connectivity contributes to learning in some languages but not in other. In particular, semantic connectivity does not explain variance in English data beyond that explained by phonological connectivity, frequency and length. This finding contrasts with the original finding in @hills2009. However, this difference might be due to our using a slightly different model (which included word length as a covariate) and a larger dataset. That said, and despite these apparent cross-linguistic differences, both phonological and semantic connectivity are significant predictors in the combined model (Figure \@ref(fig:staticAll)).

@@

This study provided an analysis of network growth during development. We compared two network growth scenarios described in the pioneering work of @steyvers2005 and @hills2009.  The first scenario, INT (originally called Preferential Attachment), described a rich-get-richer network growth model in which the current structure of the learner's internal network determines future growth; the other, EXT (originally called Preferential Acquisition) described a model in which the external, global environmental network structure determines learners' growth patterns. These two mechanisms represent two fundamentally different accounts of lexical growth: One suggests that future word knowledge is primarily shaped by the children’s past knowledge and its organization, whereas the other suggests that learning is shaped, rather, by salient properties in the input regardless of how past knowledge is organized. The present study tested the generality of previous findings by 1) investigating phonological networks together with semantic networks, 2) testing both comprehension- and production-based vocabularies, and 3) comparing the results across 10 languages.

@@

For example, in the semantic domain, growth according to EXT can be explained by a mechanism similar to cross-situational learning [@smith2008; @mcmurray2012; @yurovsky2015]. According to this mechanism, children track the co-occurrence of concrete nouns with their possible semantic referents. The referent of a word heard in only one naming situation can be ambiguous (e.g., when the word "ball" is heard for the first time in the presence of both a ball and a chair), but hearing the same word in a diversity of semantic contexts allows the learner to narrow down the set of possible word-object mappings. In our case, free association (used to determine semantic network connectivity) is related to contextual co-occurrence [@griffiths07; @fourtassi2013], meaning that highly connected words will tend to occur in a variety of speech and referential contexts.  This fact makes such words easier to learn because they have more referential disambiguating cues across learning contexts. Crucially, children can learn these words without necessarily knowing the meaning of all other words with witch they co-occur (hence the similarity with EXT). This possibility is supported by the finding that words' diversity of occurrence in child directed speech predicts their age of learning [@stella2017; @hills2010].

In the phonological case, network growth according to EXT is also compatible with a scenario whereby children are tracking low level statistical patterns, e.g., high probability sound sequences. Indeed, connectivity in the phonological network is inherently correlated with phonotactic probability [@vitevitch1999]. That is, highly connected words tend to be made of frequent sound sequences. Children are sensitive to local phonotactic regularities [@jusczyk1994] and this sensitivity might lead them to learn higher-probability words more easily [@storkel2001]. This explanation is supported by computational simulations that show how learning general phonotactics patterns create "well-worn paths" which allow the models to represent several distinct but phonologically neighboring words [@dell1993; @takac2017].
